The Lipid Interactome Repository

### 2025-03-13 LipidProbe/1-10_FattyAcid.qmd
added PI page with structure, no data

:::{.border}
::: {layout="[[-25,75], [100]]"}
![Native Fatty Acid.](/LipidProbe/Structures/fatty_acid.png)

![Trifunctional 1-10 Fatty Acid.](/LipidProbe/Structures/TF_1-10_fatty_acid.png)

>>>>

:::{.border}
::: {layout="[[-25,75], [100]]"}
![(A) Native Fatty Acid.](/LipidProbe/Structures/fatty_acid.png)

![(B) Trifunctional 1-10 Fatty Acid.](/LipidProbe/Structures/TF_1-10_fatty_acid.png)

### 2025-03-13 LipidProbe/8-3_FattyAcid.qmd
added PI page with structure, no data

:::{.border}
::: {layout="[[-25,75], [100]]"}
![Native Fatty Acid.](/LipidProbe/Structures/fatty_acid.png)

![Trifunctional 8-3 Fatty Acid.](/LipidProbe/Structures/TF_8-3_fatty_acid.png)

>>>>

:::{.border}
::: {layout="[[-25,75], [100]]"}
![(A) Native Fatty Acid.](/LipidProbe/Structures/fatty_acid.png)

![(B) Trifunctional 8-3 Fatty Acid.](/LipidProbe/Structures/TF_8-3_fatty_acid.png)

### 2025-03-13 LipidProbe/PhosphatidicAcid.qmd
added PI page with structure, no data

:::{.border}
::: {layout="[[-15,85], [100]]"}
![Native Phosphatidic Acid.](/LipidProbe/Structures/PA.png)

![Trifunctional Phosphatidic Acid.](/LipidProbe/Structures/TF_PA.png)

>>>>

:::{.border}
::: {layout="[[-15,85], [100]]"}
![(A) Native Phosphatidic Acid.](/LipidProbe/Structures/PA.png)

![(B) Trifunctional Phosphatidic Acid.](/LipidProbe/Structures/TF_PA.png)

### 2025-03-13 LipidProbe/Phosphatidylethanolamine.qmd
added PI page with structure, no data

:::{.border}
::: {layout="[[-0.01,99.99], [100]]"}
![Native Phosphatidylethanolamine.](/LipidProbe/Structures/PE.png)

![Trifunctional Phosphatidylethanolamine.](/LipidProbe/Structures/TF_PE.png)

>>>>

:::{.border}
::: {layout="[[-0.01,99.99], [100]]"}
![(A) Native Phosphatidylethanolamine.](/LipidProbe/Structures/PE.png)

![(B) Trifunctional Phosphatidylethanolamine.](/LipidProbe/Structures/TF_PE.png)

### 2025-03-13 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
added PI page with structure, no data

:::{.border}
::: {layout="[[-1.5,98.5], [100]]"}
![Native PI(3,4,5)P~3~.](/LipidProbe/Structures/PI(3,4)P2.png)

![Trifunctional PI(3,4,5)P~3~.](/LipidProbe/Structures/TF_PI(3,4,5)P3.png)

>>>>

:::{.border}
::: {layout="[[-1.5,98.5], [100]]"}
![(A) Native PI(3,4,5)P~3~.](/LipidProbe/Structures/PI(3,4)P2.png)

![(B) Trifunctional PI(3,4,5)P~3~.](/LipidProbe/Structures/TF_PI(3,4,5)P3.png)

### 2025-03-13 LipidProbe/Sphinganine.qmd
added PI page with structure, no data

:::{.border}
::: {layout="[[100], [100]]"}
![Native Sphinganine.](/LipidProbe/Structures/Sphinganine.png)

![Trifunctional Sphinganine.](/LipidProbe/Structures/TF_Sphinganine.png)

>>>>

:::{.border}
::: {layout="[[100], [100]]"}
![(A) Native Sphinganine.](/LipidProbe/Structures/Sphinganine.png)

![(B) Trifunctional Sphinganine.](/LipidProbe/Structures/TF_Sphinganine.png)

### 2025-03-13 LipidProbe/Sphingosine.qmd
added PI page with structure, no data

:::{.border}
::: {layout="[[100], [100]]"}
![Native Sphingosine.](/LipidProbe/Structures/Sphingosine.png)

![Trifunctional Sphingosine.](/LipidProbe/Structures/TF_Sphingosine.png)

>>>>

:::{.border}
::: {layout="[[100], [100]]"}
![(A) Native Sphingosine.](/LipidProbe/Structures/Sphingosine.png)

![(B) Trifunctional Sphingosine.](/LipidProbe/Structures/TF_Sphingosine.png)

### 2025-03-13 index.qmd
added PI page with structure, no data

```{=html}
<div style="text-align: center; margin: 20px;">
    <a href="LipidProbe/PhosphatidicAcid.qmd" style="text-decoration: none;">
        <button style="background-color: #3498db; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Phosphatidic Acid
        </button>
    </a>
    <a href="LipidProbe/Phosphatidylethanolamine.qmd" style="text-decoration: none;">
        <button style="background-color: #e74c3c; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Phosphatidylethanolamine
        </button>
    </a>

@@

    <a href="LipidProbe/PhosphatidylinositolBisphosphate.qmd" style="text-decoration: none;">
        <button style="background-color: #a86532; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            PI(4,5)P<sub>2</sub>
        </button>
    </a>

    <a href="LipidProbe/PhosphatidylinositolTrisphosphate.qmd" style="text-decoration: none;">
        <button style="background-color: #8732a8; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            PI(3,4,5)P<sub>3</sub>
        </button>
    </a>

    <br>
    <a href="LipidProbe/Diacylglycerol.qmd" style="text-decoration: none;">
        <button style="background-color: #3277a8; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Diacylglycerol
        </button>
    </a>

    <br>
    <a href="LipidProbe/Sphinganine.qmd" style="text-decoration: none;">
        <button style="background-color: #2ecc71; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Sphinganine
        </button>
    </a>
    <a href="LipidProbe/Sphingosine.qmd" style="text-decoration: none;">
        <button style="background-color: #eba434; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Sphingosine
        </button>
    </a>

    <br>
	<a href="LipidProbe/8-3_FattyAcid.qmd" style="text-decoration: none;">
        <button style="background-color: #ba34eb; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            8-3 Fatty Acid
        </button>
    </a>

    <a href="LipidProbe/1-10_FattyAcid.qmd" style="text-decoration: none;">
        <button style="background-color: #a83260; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            1-10 Fatty Acid
        </button>
    </a>
</div>
```

>>>>

```{=html}
<div style="text-align: center; margin: 20px;">
  <a href="LipidProbe/PhosphatidicAcid.qmd" style="text-decoration: none;">
      <button style="background-color: #97bdef; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
          Phosphatidic Acid
      </button>
  </a>
  <a href="LipidProbe/Phosphatidylethanolamine.qmd" style="text-decoration: none;">
      <button style="background-color: #2986cc; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
          Phosphatidylethanolamine
      </button>
  </a>

@@

    <a href="LipidProbe/Phosphatidylinositol.qmd" style="text-decoration: none;">
        <button style="background-color: rgb(231, 109, 104); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Phosphatidylinositol (PI)
        </button>
    </a>

    <a href="LipidProbe/PhosphatidylinositolBisphosphate.qmd" style="text-decoration: none;">
        <button style="background-color: #f14334; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            PI(4,5)P<sub>2</sub>
        </button>
    </a>

    <a href="LipidProbe/PhosphatidylinositolTrisphosphate.qmd" style="text-decoration: none;">
        <button style="background-color:rgb(223, 21, 21); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            PI(3,4,5)P<sub>3</sub>
        </button>
    </a>

    <br>
    <a href="LipidProbe/Diacylglycerol.qmd" style="text-decoration: none;">
        <button style="background-color: #2ecc71; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Diacylglycerol
        </button>
    </a>

    <br>
    <a href="LipidProbe/Sphinganine.qmd" style="text-decoration: none;">
        <button style="background-color:rgb(101, 46, 204); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Sphinganine
        </button>
    </a>
    <a href="LipidProbe/Sphingosine.qmd" style="text-decoration: none;">
        <button style="background-color:rgb(202, 52, 235); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Sphingosine
        </button>
    </a>

    <br>
	<a href="LipidProbe/8-3_FattyAcid.qmd" style="text-decoration: none;">
        <button style="background-color:rgb(235, 177, 52); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            8-3 Fatty Acid
        </button>
    </a>

    <a href="LipidProbe/1-10_FattyAcid.qmd" style="text-decoration: none;">
        <button style="background-color:rgb(237, 111, 38); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            1-10 Fatty Acid
        </button>
    </a>
</div>
```
